New first figure

### 2021-05-06 manuscript/bef_stability/fig1_biomass_network.Rmd
Reviewed according to Maud's comments

```{r}
myload(metaweb_analysis,  dir = mypath("data"))
sp_color <- set_color_species(
  node_list = colnames(metaweb_analysis$metaweb),
  resource_list = metaweb_analysis$resource
)
node_sp <- str_extract(colnames(metaweb_analysis$metaweb), "[A-Z|a-z]*")
sp_color[node_sp]

TL <- NetIndices::TrophInd(metaweb_analysis$metaweb)$TL
PlotWeb(
  TL = TL,
  webTL = metaweb_analysis$metaweb,
  colnode = sp_color[node_sp],
  abund = 1,
  collink="grey70",
  scale_abun = .005
) 
```

>>>>

```{r}
myload(metaweb_analysis,  dir = mypath("data"))
sp_color <- set_color_species(
  node_list = colnames(metaweb_analysis$metaweb),
  resource_list = metaweb_analysis$resource
)
node_sp <- str_extract(colnames(metaweb_analysis$metaweb), "[A-Z|a-z]*")
sp_color[node_sp]
names(sp_color)[names(sp_color) %in% meta$resource] <- 
  c("detritivore", "biofilm", "phytobenthos", "macrophage", "phytoplankton", "zooplankton", "zoobenthos")

TL <- NetIndices::TrophInd(metaweb_analysis$metaweb)$TL

dev.new(width = 5, height = 7, units = "in")
# i3: mod + shift + space

png(
  filename = mypath("manuscript/bef_stability/figs",
    "metaweb2.png"), 
  units = "in",
  width = 5,
  height = 7,
  pointsize = 12*96/72,
  res = 200 
)
org_par <- par(
  mar = c(4, 0, 0, 0) + 0,
  oma = c(0, 0, 0, 0),
  xpd = NA 
)
PlotWeb(
  TL = TL,
  webTL = metaweb_analysis$metaweb,
  colnode = sp_color[node_sp],
  abund = 6,
  collink="grey90",
  scale_abun = .01
)

legend(
#  x      = 0.031,
#  y      = 4,
  x      = "bottom",
  inset = -.15,
  legend = names(sp_color),
  pch    = 21,
  col    = "#777777",
  pt.bg  = sp_color,
  pt.cex = 0.7,
  cex    = .5,
  bty    = "n",
  x.intersp = 1,
  text.width = .1, 
  ncol   = 6

)

dev.off()
par(org_par)
```
